Quartzite Complexities: Non-destructive analysis of bifacial points from Västerbotten, Sweden

### 2023-05-16 analysis/paper/paper.qmd
Added reference

Cluster 2 is distinguished by a higher ~22~Ti, ~26~Fe and ~40~Zr content. It mainly features samples with a dark hue, with the few samples from the light group being grey in colour and arguably somewhere in between a “dark” or “light” hue. ~13~Al and ~19~K is similarly higher in cluster 2 than cluster 3, which is in turn marked by its, on average, lower elemental content than the other two clusters. As ~13~Al and ~19~K are indicative of a sedimentary depositional context that has been subject to metamorphism (REF FROM JOHAN), and the cluster with higher values may thus indicate samples with a different grade of metamorphism. Cluster 3 features a more limited range of values between the samples and includes all the brecciated quartz.

>>>>

Cluster 2 is distinguished by a higher ~22~Ti, ~26~Fe and ~40~Zr content. It mainly features samples with a dark hue, with the few samples from the light group being grey in colour and arguably somewhere in between a “dark” or “light” hue. ~13~Al and ~19~K is similarly higher in cluster 2 than cluster 3, which is in turn marked by its, on average, lower elemental content than the other two clusters. As ~13~Al and ~19~K are indicative of a sedimentary depositional context that has been subject to metamorphism [@hazen_morrison2022], and the cluster with higher values may thus indicate samples with a different grade of metamorphism. Cluster 3 features a more limited range of values between the samples and includes all the brecciated quartz.
